Sampling Strategies in Decisions from Experience

### 2021-12-06 manuscript.Rmd
Start introduction text

---
title: 'Sampling Strategies in Decisions from Experience'
author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
bibliography: references_sampling-in-dfe.bib
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    fig_width: 10
    fig_height: 7
csl: apa.csl
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

```{r}
# load packages
pacman::p_load(tidyverse, 
               knitr, 
               ggbeeswarm,
               scico # for scientific color palettes
               )
```

# Introduction

# Sampling in Decisions from Experience

@@

@@

trial_length %>%
  ggplot(aes(x = s, y = med)) +
  geom_jitter(color = "#CECECE", size = 3) +
  geom_point(data = trial_length_s, aes(color = s), size = 3) +
  geom_path(data = trial_length_s, aes(color = s)) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .1)) + 
  scale_y_continuous(breaks = seq(0, 120, 10)) +
  labs(title = "Trial Length", 
       x ="Switching Probability",
       y = "Median Trial Length", 
       color="Switching Probability") + 
  theme_minimal()
```

@@

@@

cpt_long %>% 
  filter(parameter == "gamma" | parameter == "delta") %>% 
  ggplot(aes(x = s, y = mean)) +
  geom_density_2d_filled(contour_var = "ndensity") + 
  scale_fill_scico_d(palette = "buda") +
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
  labs(x ="Switching Probability",
       y = "Parameter Value",  
       fill="Density") + 
  facet_grid(parameter~a) + 
  theme_minimal()
```

@@

# alpha
cpt_wide %>% 
  ggplot(aes(x = s, y = alpha, color = s)) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(breaks = seq(0, 2, .2)) +
  facet_grid(boundary~a, switch = "y") +
  labs(title = expression(alpha),
       x ="Switching Probability",
       y = expression(alpha), 
       color="Switching Probability") + 
  theme_minimal()

```

@@

# Acknowledgements

@@

@@

```{r message=FALSE}
gambles <- read_csv("data/gambles/sr_subset.csv")
gambles %>% kable()
```

>>>>

---
title             : "Sampling Strategies in Decisions from Experience"
shorttitle        : "Sampling in Decisions from Experience"

header-includes: 
  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1]{Linus Hof}
  - \authorsaffiliations{{Department of Psychology, Heidelberg University}}

author: 
  - name          : "Linus Hof"
    affiliation   : "1"
    corresponding : yes    
    address       : "Department of Psychology, Heidelberg University, Hauptstraße 47-51, 69117 Heidelberg, Germany"
    email         : "linushof@posteo.de"

note: | 
  **Unsubmitted draft created from the commit with the hash**: ``r repro::current_hash()``

authornote: |
 This is a dynamic document which can be reproduced from the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe.

 The current version of this manuscript is prepared for submission as a master's thesis. A modified later version might be prepared together with co-authors and submitted for peer-review.

abstract: |
  Add abstract

keywords          : ""
wordcount         : ""

bibliography      : ["references_sampling-in-dfe.bib"]
csl               : apa.csl

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
linkcolor         : "blue"
mask              : no
draft             : no

classoption       : "man"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

```{r}
# load packages
pacman::p_load(tidyverse, 
               knitr, 
               ggbeeswarm,
               scico, # for scientific color palettes
               papaja)
```

<!-- Computational level -->

Decision making is an information-processing problem whose solution requires a selection among choice alternatives. 
The basic structure of the problem may be modeled by the inclusion map $\iota : A' \mapsto A$, indicating that decision making is a *process* that starts from an initial set $A$, including all choice alternatives, and stops at a proper subset $A' \subset A$, only including the chosen alternatives. 
Given that this selection process is systematic---as opposed to random---the chosen alternatives in $A'$ possess the same *property* or combination of several properties which the other alternatives in the complementary subset $A \setminus A'$ do not possess.
We may label the properties that serve to distinguish between the chosen and non-chosen alternatives as *selection criteria*.

<!-- Algorithmic Level -->

Thus, a rather important part---although by far not the only one---of the computation that connects the initial set with its subset is the comparison of the properties of the choice alternatives against some selection criteria. 
At the algorithmic level, such comparisons require an explicit description of the properties using a representation system which is useful to the processing system, i.e., a living organism or a computer [@marrRepresentationRecognitionSpatial1978; @marrVisionComputationalInvestigation1982]. 
In quite many cases, however, the selection process is not restricted to one particular representation system but a number of different representations can be used to describe the properties of a given set of choice alternatives. 
E.g., an important difference that has emerged in behavioral decision research is whether the probability of a risky outcome is readily described as a decimal number, ratio, or percentage or whether it must be inferred from the relative frequency of occurrence of the particular outcome in a collection of random variables [@hertwigDescriptionexperienceGapRisky2009].

<!-- Samples as representation -->

@@

```{r fig.cap="Test"}

@@

trial_length %>%
  ggplot(aes(x = s, y = med)) +
  geom_jitter(color = "#CECECE", size = 3) +
  geom_point(data = trial_length_s, aes(color = s), size = 3) +
  geom_path(data = trial_length_s, aes(color = s)) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .1)) + 
  scale_y_continuous(breaks = seq(0, 120, 10)) +
  labs(title = "Trial Length", 
       x ="Switching Probability",
       y = "Median Trial Length", 
       color="Switching Probability") + 
  theme_apa()
```

@@

```{r fig.cap="test 2"}

@@

cpt_long %>% 
  filter(parameter == "gamma" | parameter == "delta") %>% 
  ggplot(aes(x = s, y = mean)) +
  geom_density_2d_filled(contour_var = "ndensity") + 
  scale_fill_scico_d(palette = "buda") +
  scale_color_scico_d(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
  labs(x ="Switching Probability",
       y = "Parameter Value",  
       fill="Density") + 
  facet_grid(parameter~a) + 
  theme_apa()
```

@@

# alpha
cpt_wide %>% 
  ggplot(aes(x = s, y = alpha, color = s)) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(breaks = seq(0, 2, .2)) +
  facet_grid(boundary~a, switch = "y") +
  labs(title = expression(alpha),
       x ="Switching Probability",
       y = expression(alpha), 
       color="Switching Probability") + 
  theme_minimal()
```

@@

@@

# Software

@@

```{r message=FALSE}
gambles <- read_csv("data/gambles/sr_subset.csv")
gambles %>% apa_table()
```
